The given cross sections in the reactions may not be linearized. As a result, they can be easily summed or accumulated. 

\section{Algorithm}
The ENDF interpolation tabular data points are divided into regions, each of which uses an integer from 1 to 5 to indicate the method of interpolation. 

\subsection{Histogram}
If the interpolation law number is 1, the method of interpolation represents a histogram. The points on the region boundaries will remain the same, and each point internal to the region will be accompanied by another point with a $y$ value equal to the previous point. 

\subsection{Linear-Linear Interpolation}
If the interpolation law number is 2, the method of interpolation is linear to linear. All points will remain the same. No modifications will be applied.

\subsection{Other Laws of Interpolation}
If the interpolation law number betweens 3 and 5, additional data points may be necessary to be inserted into the region to make the error of linearization below a certain level of requirement, for example $0.1\%$. The algorithm applied is called the method of inverted stack. 

\subsection{Removal of Duplicated Points}
Sometimes, the data points after the linearization may have duplications. That is the case that for two points: $(x_1,y_1)$ and $(x_2,y_2)$, we have:
\begin{eqnarray}
x_1 &=& x_2,\\
|y_1-y_2| &<& \epsilon,
\end{eqnarray}
where $\epsilon$ is small value such as $1\times10^{-10}$ barn.

\section{C++ Data Structures \& APIs}
The XLS class has a static method called `linearizeENDFInterpFunc', which takes a ENDF interpolation table function and return a vector of cross section data points.
\begin{verbatim}
struct XLSXsecPair {
    double energyEv  = 0.;
    double sigmaBarn = 0.;
};

// Discontinuity of cross section may present
struct XLSXsec {
    std::vector<XLSXsecPair> xspairs;
};

// The cross section linearization system will take
// an ENDFInterpolationFunction representation
// of a cross section data, and linearlize it
// into an XLSXsec data format, the tolerance in the fraction
// of the relative error is given
class XLS {
public:
    static XLSXsec linearizeENDFInterpFunc
    (const ENDFInterpolationFunction& endf, double tol);
};
\end{verbatim}